Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/intro.tex
revised intro

Our evaluation of Grappa shows that it runs several graph-crunching
applications (classic examples of irregular behavior) very efficiently on a
commodity cluster. Our yardstick for comparison is the XMT hardware itself.
Using the same number of processors (in our case cores on a single multicore
processor), Grappa is in the same ballpark as the XMT: on some graphs, such as
the \checkme{WTF} Grappa is \checkme{2X} faster, while on others, such as the
\checkme{WTF2} Grappa is \checkme{2X} slower. In Section~\ref{sec:results} we
explore the factors that underpin this performance. But most importantly,
application performance \emph{scales} with Grappa. For significantly less real
world cost, users can \emph{add} more processors to a commodity cluster and
easily outperform the XMT hardware on graph processing, while still saving
significant dollars.

>>>>

Our evaluation of Grappa shows that it runs several graph-crunching
applications (classic examples of irregular behavior) very efficiently
on a commodity cluster. Our yardstick for comparison is the XMT hardware
itself. Using the same number of network interfaces, Grappa is in the
same ballpark as the XMT: For unbalanced tree search, Grappa is over 3X
faster and shows greatly improved scalability; conversely, for breadth
first search and betweenness centrality Grappa is 2.5X slower.  In
Section~\ref{sec:results} we explore the factors that underpin this
performance. Most importantly, however, for significantly less real
world cost, users can \emph{add} significantly more processors to a
commodity cluster than an XMT machine and use Grappa to achieve scalable
performance.
